**The Place of Interoception and Theory of Mind in Deception**

### 2021-12-07 index.Rmd
tidy up
move files to preprocessing, rename scripts folder, rename variables in data processing

df <- read.csv("data/data_combined.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         condition = as.factor(condition),
         item = as.factor(item),
         style = as.factor(style),
         instruction = as.factor(instruction)) |> 
  #TODO: This renaming should be done at the preprocessing stage
  rename("Participant" = "ID",
         "Condition" = "condition",
         "Item" = "item",
         "Phrasing" = "style",
         "Answer" = "instruction",
         "YONI_Total" = "yoni_total",
         "YONI_Affective" = "yoni_affective",
         "YONI_Cognitive" = "yoni_cognitive",
         "YONI_Physical" = "yoni_physical",
         "BES_Total" = "BES_total",
         "BES_Cognitive" = "BES_cognitive",
         "BES_Affective" = "BES_affective",
         "HCT_Confidence" = "HCT_confidence",
         "HCT_Accuracy" = "HCT_accuracy",
         "HCT_Awareness" = "HCT_awareness",
         "MAIA_Total" = "MAIA_total",
         "MAIA_AttentionRegulation" = "MAIA_attention_regulation",
         "MAIA_BodyListening" = "MAIA_body_listening",
         "MAIA_EmotionalAwareness" = "MAIA_emotional_awareness",
         "MAIA_NotDistracting" = "MAIA_not_distracting",
         "MAIA_NotWorrying" = "MAIA_not_worrying",
         "MAIA_Noticing" = "MAIA_noticing",
         "MAIA_SelfRegulation" = "MAIA_self_regulation",
         "MAIA_Trusting" = "MAIA_trusting",
         "LIE_Ability" = "lie_ability",
         "LIE_Frequency" = "lie_frequency",
         "LIE_Negativity" = "lie_negativity",
         "LIE_Contextuality" = "lie_contextuality",
         "Confidence" = "DT_confidence",
         "RT" = "DT_RT") |> 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH")) |> 
  select(-HCT_guess, -HCT_noguess, -HCT_onebreath)

>>>>

df <- read.csv("data/data_combined_wPhysio.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  rename("HeartRate" = "ECG_Rate_MeanRaw_1.5_2.5s") |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

# Adjustments for beta models
df$Confidence[df$Confidence == 1] <- 0.99999
df$Confidence[df$Confidence == 0] <- 0.00001

### 2021-12-07 preprocessing/data processing.Rmd
tidy up
move files to preprocessing, rename scripts folder, rename variables in data processing

mydata <- read.csv('../../data/data_questionnaire/Demographics.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34, 36)]

@@

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61,104), -c(4,5,7:38,42:47)]
  mydata <- rbind(mydata, df_sub)
}

@@

results <- data %>%
  group_by(ID, condition) %>%
  summarise(total = sum(answer)) %>%
  pivot_wider(names_from = condition, values_from = total) %>%
  mutate(yoni_total = affect+cognitive+physical) %>%
  rename(yoni_affective = affect,
         yoni_cognitive = cognitive,
         yoni_physical = physical)

@@

mydata <- read.csv("../../data/data_questionnaire/BES.csv", stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

@@

  mutate(BES_cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20, 
         BES_affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18,
         BES_total = BES_cognitive+BES_affective) %>%

@@

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(hbcount_reported = heartbeatresponse.text,
       HCT_confidence = confidenceslider.response,
       HCT_confidenceRT = confidenceslider.rt,
       ID = participant) %>%

@@

  mutate(hbcount_reported = str_remove_all(hbcount_reported, "Enter Number")) %>% 
  mutate(hbcount_reported = as.numeric(hbcount_reported),
         HCT_confidence = as.numeric(HCT_confidence)) %>%

@@

data <- data %>% 
  select(-c(participant, task)) %>% 
  mutate(numerator = hbcount_real - hbcount_reported) %>% 
  mutate(numerator = abs(numerator)) %>% 
  mutate(denominator = (hbcount_real + hbcount_reported)/2) %>% 
  mutate(HCT_accuracy = 1 - numerator/denominator)

df_awareness <- data.frame()
for(participant in unique(data$ID)) {
  conf <- data[data$ID == participant, "HCT_confidence"]
  acc <- data[data$ID == participant, "HCT_accuracy"]
  awa <- cor(conf, acc, use = "pairwise.complete.obs")
  df_awareness <- rbind(df_awareness,
                       data.frame(ID = participant,
                                  HCT_awareness = awa))
}

data <- merge(data, df_awareness, by = "ID")
results <- data %>% 
  select(c(ID, HCT_confidence, HCT_accuracy, HCT_awareness)) %>% 
  group_by(ID) %>%
  summarise_all(mean, na.rm = TRUE)

parttwo <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(1:5, 9), -c(1:13, 16:19, 22:25, 28:31, 33:38)]  
  parttwo <- rbind(parttwo, df_sub)
}

parttwo <- parttwo %>% 
  rename(guess = key_guess.keys,
         guessRT = key_guess.rt,
         noguess = key_noguess.keys,
         noguessRT = key_noguess.rt,
         onebreath = key_noguess_perturbed.keys,
         onebreathRT = key_noguess_perturbed.rt,
         ID = participant) %>% 
  group_by(ID) %>% 
  summarise_all(funs(trimws(paste(., collapse = ''))))

parttwo <- parttwo %>% 
  mutate(HCT_guess = str_count(parttwo$guess, "space"),
         HCT_noguess = str_count(parttwo$noguess, "space"),
         HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
  select(c(ID, HCT_guess, HCT_noguess, HCT_onebreath))

results <- left_join(results, parttwo)

@@

mydata <- read.csv('../../data/data_questionnaire/MAIA2.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

@@

  mutate(MAIA1 = (Q1+Q2+Q3+Q4)/4, MAIA2 = (Q5+Q6+Q7+Q8+Q9+Q10)/6, MAIA3 = (Q11+Q12+Q13+Q14+Q15)/5, MAIA4 = (Q16+Q17+Q18+Q19+Q20+Q21+Q22)/7,
        MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
  mutate(MAIA_total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
  rename(MAIA_noticing = MAIA1,
         MAIA_not_distracting = MAIA2,
         MAIA_not_worrying = MAIA3,
         MAIA_attention_regulation = MAIA4,
         MAIA_emotional_awareness = MAIA5,
         MAIA_self_regulation = MAIA6,
         MAIA_body_listening = MAIA7,
         MAIA_trusting = MAIA8) %>%

@@

mydata <- read.csv('../../data/data_questionnaire/Lie Scale.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

@@

  mutate(lie_ability = (Q4+Q5+Q6+Q7)/4, 
         lie_frequency = (Q1+Q2+Q3+Q8)/4, 
         lie_negativity = (Q9+Q11+Q13+Q16)/4, 
         lie_contextuality = (Q10+Q12+Q14+Q15)/4) %>%

@@

write.csv(results, file = "liescale_processed.csv", row.names=FALSE)
```

@@

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(trial = c(1:80),
           condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

inclusion <- read.csv("../final_processing/Errors.csv") %>%
  rename(ID = ï..participant,
         trial = Trial,
         inclusion = Inclusion,
         inclusion2 = Inclusion2)

data <- mydata %>% 
  rename(item = V1,
       style = V2,
       instruction = V3,
       question = V4,
       social_start = V29,
       social_stop = V31,
       DT_confidence = V35,
       DT_confidenceRT = V36,
       polyg_start = V43,
       polyg_stop = V45,
       ID = V47) %>%

  mutate(DT_confidence = as.numeric(DT_confidence),
         social_start = as.numeric(social_start),
         social_stop = as.numeric(social_stop),
         polyg_start = as.numeric(polyg_start),
         polyg_stop = as.numeric(polyg_stop),
         ID = as.numeric(ID)) %>%
  mutate(DT_RT = ifelse(condition == "Social", social_stop - social_start,
         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

  left_join(inclusion) %>%
  select(ID, trial, condition, inclusion, inclusion2, everything()) # move columns to front

results <- data %>%
  group_by(ID, instruction, style) %>%
  summarise(DT_RT_avg = mean(DT_RT, na.rm = TRUE),
            DT_confidence_avg = mean(DT_confidence, na.rm = TRUE))

write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
write.csv(results, file = "deceptiontask_processed.csv", row.names=FALSE)
```

```{r combine data}
qn <- paste0("Q", 1:40)
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("liescale_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG))

write.csv(data_combined, file = "../../data/data_combined.csv", row.names = FALSE)
```

>>>>

mydata <- read.csv('../data/data_questionnaire/Demographics.csv', stringsAsFactors = FALSE)[-c(1:2), -c(1:17, 30, 32, 34, 36)]

@@

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/yoni/", participant, "_untitled.csv"))[-c(1:3,28,61,104), -c(4,5,7:38,42:47)]
  mydata <- rbind(mydata, df_sub)
}

@@

results <- data %>%
  group_by(ID, condition) %>%
  summarise(total = sum(answer)) %>%
  pivot_wider(names_from = condition, values_from = total) %>%
  mutate(YONI_Total = affect+cognitive+physical) %>%
  rename(YONI_Affective = affect,
         YONI_Cognitive = cognitive,
         YONI_Physical = physical)

@@

mydata <- read.csv("../data/data_questionnaire/BES.csv", stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

@@

  mutate(BES_Cognitive = Q3+Q6+Q9+Q10+Q12+Q14+Q16+Q19+Q20, 
         BES_Affective = Q1+Q2+Q4+Q5+Q7+Q8+Q11+Q13+Q15+Q17+Q18,
         BES_Total = BES_Cognitive+BES_Affective) %>%

@@

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(6:9), -c(1, 3:8, 12:31, 33:38)]  
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(hbcount_reported = heartbeatresponse.text,
       HCT_Confidence = confidenceslider.response,
       HCT_ConfidenceRT = confidenceslider.rt,
       ID = participant) %>%

@@

  mutate(hbcount_reported = str_remove_all(hbcount_reported, "Enter Number")) %>% 
  mutate(hbcount_reported = as.numeric(hbcount_reported),
         HCT_Confidence = as.numeric(HCT_Confidence)) %>%

@@

data <- data %>% 
  select(-c(participant, task)) %>% 
  mutate(numerator = hbcount_real - hbcount_reported) %>% 
  mutate(numerator = abs(numerator)) %>% 
  mutate(denominator = (hbcount_real + hbcount_reported)/2) %>% 
  mutate(HCT_Accuracy = 1 - numerator/denominator)

df_awareness <- data.frame()
for(participant in unique(data$ID)) {
  conf <- data[data$ID == participant, "HCT_Confidence"]
  acc <- data[data$ID == participant, "HCT_Accuracy"]
  awa <- cor(conf, acc, use = "pairwise.complete.obs")
  df_awareness <- rbind(df_awareness,
                       data.frame(ID = participant,
                                  HCT_Awareness = awa))
}

data <- merge(data, df_awareness, by = "ID")
results <- data %>% 
  select(c(ID, HCT_Confidence, HCT_Accuracy, HCT_Awareness)) %>% 
  group_by(ID) %>%
  summarise_all(mean, na.rm = TRUE)

# parttwo <- data.frame()
# for (participant in list.files("../data/data_experimental")) {
#   df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/heartbeat/", participant, "_heartbeat.csv"))[-c(1:5, 9), -c(1:13, 16:19, 22:25, 28:31, 33:38)]  
#   parttwo <- rbind(parttwo, df_sub)
# }
#   
# parttwo <- parttwo %>% 
#   rename(guess = key_guess.keys,
#          guessRT = key_guess.rt,
#          noguess = key_noguess.keys,
#          noguessRT = key_noguess.rt,
#          onebreath = key_noguess_perturbed.keys,
#          onebreathRT = key_noguess_perturbed.rt,
#          ID = participant) %>% 
#   group_by(ID) %>% 
#   summarise_all(funs(trimws(paste(., collapse = ''))))
# 
# parttwo <- parttwo %>% 
#   mutate(HCT_guess = str_count(parttwo$guess, "space"),
#          HCT_noguess = str_count(parttwo$noguess, "space"),
#          HCT_onebreath = str_count(parttwo$onebreath, "space")) %>% 
#   select(c(ID, HCT_guess, HCT_noguess, HCT_onebreath))
# 
# results <- left_join(results, parttwo)

@@

mydata <- read.csv('../data/data_questionnaire/MAIA2.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

@@

  mutate(MAIA1 = (Q1+Q2+Q3+Q4)/4, MAIA2 = (Q5+Q6+Q7+Q8+Q9+Q10)/6, MAIA3 = (Q11+Q12+Q13+Q14+Q15)/5, MAIA4 = (Q16+Q17+Q18+Q19+Q20+Q21+Q22)/7,
        MAIA5 = (Q23+Q24+Q25+Q26+Q27)/5, MAIA6 = (Q28+Q29+Q30+Q31)/4, MAIA7 = (Q32+Q33+Q34)/3, MAIA8 = (Q35+Q36+Q37)/3) %>% 
  mutate(MAIA_Total = (MAIA1+MAIA2+MAIA3+MAIA4+MAIA5+MAIA6+MAIA7+MAIA8)/8) %>%
  rename(MAIA_Noticing = MAIA1,
         MAIA_NotDistracting = MAIA2,
         MAIA_NotWorrying = MAIA3,
         MAIA_AttentionRegulation = MAIA4,
         MAIA_EmotionalAwareness = MAIA5,
         MAIA_SelfRegulation = MAIA6,
         MAIA_BodyListening = MAIA7,
         MAIA_Trusting = MAIA8) %>%

@@

mydata <- read.csv('../data/data_questionnaire/Lie Scale.csv', stringsAsFactors = FALSE)[-c(1, 2), -c(1:17)]

@@

  mutate(LIE_Ability = (Q4+Q5+Q6+Q7)/4, 
         LIE_Frequency = (Q1+Q2+Q3+Q8)/4, 
         LIE_Negativity = (Q9+Q11+Q13+Q16)/4, 
         LIE_Contextuality = (Q10+Q12+Q14+Q15)/4) %>%

@@

write.csv(results, file = "lie_processed.csv", row.names=FALSE)
```

@@

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(Trial = c(1:80),
           Condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(Item = V1,
       Phrasing = V2,
       Answer = V3,
       Question = V4,
       social_start = V29,
       social_stop = V31,
       Confidence = V35,
       ConfidenceRT = V36,
       polyg_start = V43,
       polyg_stop = V45,
       ID = V47) %>%

  mutate(Confidence = as.numeric(Confidence),
         social_start = as.numeric(social_start),
         social_stop = as.numeric(social_stop),
         polyg_start = as.numeric(polyg_start),
         polyg_stop = as.numeric(polyg_stop),
         ID = as.numeric(ID)) %>%
  mutate(RT = ifelse(Condition == "Social", social_stop - social_start,
         ifelse(Condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

  select(ID, Trial, Condition, everything()) # move columns to front

write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
```

```{r combine data}
qn <- paste0("Q", 1:40)
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("lie_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
  rename(Participant = ID) %>% 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH"))

write.csv(data_combined, file = "../data/data_combined.csv", row.names = FALSE)
```
